The `zoon` R package for reproducible and shareable species distribution modelling

### 2016-03-31 ms.Rmd
Set the seed.

@@

```{r fengworkflow, eval = TRUE, results = 'hide', message = FALSE, fig.cap = fengworkcap}
Feng_Papes <- 
  workflow(occurrence = SpOcc('Dasypus novemcinctus',
                              extent = c(-130, -20, -60, 60)),
            covariate = Bioclim(extent = c(-130, -20, -60, 60),
                                layers = c(1:4, 6, 9, 10, 12, 15)),
              process = Chain(Clean, 
                              MESSMask,  
                              Background(n = 1000, bias = 200), 
                              Crossvalidate(k = 5)),
                model = MaxEnt,
               output = Chain(PerformanceMeasures, PrintMap))

>>>>

set.seed(1633)

@@

```{r fengworkflow, eval = TRUE, results = 'hide', message = FALSE, fig.cap = fengworkcap}
Feng_Papes <- 
  workflow(occurrence = SpOcc('Dasypus novemcinctus',
                              extent = c(-130, -20, -60, 60)),
            covariate = Bioclim(extent = c(-130, -20, -60, 60),
                                layers = c(1:4, 6, 9, 10, 12, 15)),
              process = Chain(Clean, 
                              MESSMask,  
                              Background(n = 10000, bias = 200), 
                              Crossvalidate(k = 5)),
                model = MaxEnt,
               output = Chain(PerformanceMeasures, PrintMap))
